Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?

### 2018-09-18 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Add QLD scraper

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to impose structure such as correlation between days. We then construct a **[XYZ]** model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).

@@

Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments. A forecasting model is then used to construct a counterfactual. Our work fits into a growing literature that considers text as a input to more usual quantitative techniques, rather than requiring separate analysis. While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.

@@

| Parliament       | House                    | Years used | Number of records |
|:------|-----:|---------:|------:|
| Commonwealth      | House of Representatives | 1901 - 2017 | 7,873 |
|                   | Senate                   | 1901 - 2017 | **[TBD]** |
| Queensland        | Legislative Assembly     | 1860 - 2017 | **[TBD]** |
|                   | Legislative Council      | 1860 - 1922 | **[TBD]** |
| New South Wales[^2]   | Legislative Assembly     | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council     | 1856 - 2017 | **[TBD]** |
| Victoria          | Legislative Assembly     | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council      | 1851 - 2017 | **[TBD]** |
| Tasmania[^3]      | House of Assembly        | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council      | 1856 - 2017 | **[TBD]** |
| South Australia[^4] | House of Assembly       | 1857 - 2017 | **[TBD]** |
|                   | Legislative Council       | 1840 - 2017 | **[TBD]** |
| Western Australia[^5] | Legislative Assembly  | 1890 - 2017 | **[TBD]** |
|                   | Legislative Council       | 1832 - 2017 | **[TBD]** |

>>>>

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We then examine the effect of various events using a discrete choice model. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to impose structure such as correlation between days and changes over time, and for dimension reduction. We then use a discrete choice model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).

@@

Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments. Our use of a discrete choice model allows us construct a counterfactual. Our work fits into a growing literature that considers text as a input to more usual quantitative techniques, rather than requiring separate analysis. While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.

@@

| Parliament       | House                    | Years used | Number of records |
|:------|-----:|---------:|------:|
| Commonwealth      | House of Representatives | 1901 - 2017 | 7,873 |
|                   | Senate                   | 1901 - 2017 | **[TBD]** |
| Queensland        | Legislative Assembly     | 1860 - 2017 | 9,699 |
|                   | Legislative Council      | 1860 - 1922 | 4,156 |
| New South Wales[^2]   | Legislative Assembly | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council     | 1856 - 2017 | **[TBD]** |
| Victoria          | Legislative Assembly     | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council      | 1851 - 2017 | **[TBD]** |
| Tasmania[^3]      | House of Assembly        | 1856 - 2017 | **[TBD]** |
|                   | Legislative Council      | 1856 - 2017 | **[TBD]** |
| South Australia[^4] | House of Assembly       | 1857 - 2017 | **[TBD]** |
|                   | Legislative Council       | 1840 - 2017 | **[TBD]** |
| Western Australia[^5] | Legislative Assembly  | 1890 - 2017 | **[TBD]** |
|                   | Legislative Council       | 1832 - 2017 | **[TBD]** |

### 2018-09-18 outputs/docs/events/svm-rmarkdown-article-example.tex
Add QLD scraper

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
suggestions. \textbf{Version as of}: September 16, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\noindent We use a structural text model to explore the effect of various events
on what was said in Australian state and federal parliaments from the
mid-1800s through to 2017. We find that: 1) changes of government are
associated with topic changes only when there is also a change in the
party in power; 2) polling results appear dissociated from parliamentary
topics; 3) economic changes, such as financial crises have a significant
effect; and 4) other events, such as an unexpected attack tend not to
have a prolonged change.

@@

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016} to
impose structure such as correlation between days. We then construct a
\textbf{{[}XYZ{]}} model to examine changes at various types of events,
including: changes in government; changes in the political environment
(as defined by polling or other results); changes in economic
conditions; and other significant events (such as the 9/11 attacks or
the Bali bombings).

@@

\begin{longtable}[]{@{}lrrr@{}}
\toprule
Parliament & House & Years used & Number of records\tabularnewline
\midrule
\endhead
Commonwealth & House of Representatives & 1901 - 2017 &
7,873\tabularnewline
& Senate & 1901 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Queensland & Legislative Assembly & 1860 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1860 - 1922 & \textbf{{[}TBD{]}}\tabularnewline
New South Wales\footnote{The NSW Legislative Council was established
  earlier than 1856, however the earlier Hansard records have not been
  through an independent OCR process and were not used in this paper.
  However, the Google Tesseract OCR engine as implemented by
  \citet{Ooms2018tesseract} provided useful data and these could be used
  in the future.} & Legislative Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Victoria & Legislative Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1851 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Tasmania\footnote{\textbf{{[}Update this, depending on final Tassie
  records{]}}.} & House of Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
South Australia\footnote{\textbf{{[}Update this, depending on final SA
  records{]}}.} & House of Assembly & 1857 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1840 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Western Australia\footnote{\textbf{{[}Update this, depending on final WA
  records{]}}.} & Legislative Assembly & 1890 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1832 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
\bottomrule
\end{longtable}

>>>>

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
suggestions. \textbf{Version as of}: September 17, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\noindent We use a structural text model to explore what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We
then examine the effect of various events using a discrete choice model.
We find that: 1) changes of government are associated with topic changes
only when there is also a change in the party in power; 2) polling
results appear dissociated from parliamentary topics; 3) economic
changes, such as financial crises have a significant effect; and 4)
other events, such as an unexpected attack tend not to have a prolonged
change.

@@

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016} to
impose structure such as correlation between days and changes over time,
and for dimension reduction. We then use a discrete choice model to
examine changes at various types of events, including: changes in
government; changes in the political environment (as defined by polling
or other results); changes in economic conditions; and other significant
events (such as the 9/11 attacks or the Bali bombings).

@@

\begin{longtable}[]{@{}lrrr@{}}
\toprule
Parliament & House & Years used & Number of records\tabularnewline
\midrule
\endhead
Commonwealth & House of Representatives & 1901 - 2017 &
7,873\tabularnewline
& Senate & 1901 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Queensland & Legislative Assembly & 1860 - 2017 & 9,699\tabularnewline
& Legislative Council & 1860 - 1922 & 4,156\tabularnewline
New South Wales\footnote{The NSW Legislative Council was established
  earlier than 1856, however the earlier Hansard records have not been
  through an independent OCR process and were not used in this paper.
  However, the Google Tesseract OCR engine as implemented by
  \citet{Ooms2018tesseract} provided useful data and these could be used
  in the future.} & Legislative Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Victoria & Legislative Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1851 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Tasmania\footnote{\textbf{{[}Update this, depending on final Tassie
  records{]}}.} & House of Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
South Australia\footnote{\textbf{{[}Update this, depending on final SA
  records{]}}.} & House of Assembly & 1857 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1840 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Western Australia\footnote{\textbf{{[}Update this, depending on final WA
  records{]}}.} & Legislative Assembly & 1890 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1832 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
\bottomrule
\end{longtable}
